---
title: Introducing the topicanalysis package
output: github_document
---

[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![Travis-CI Build Status](https://api.travis-ci.org/PolMine/topicanalysis.svg?branch=master)](https://travis-ci.org/PolMine/topicanalysis)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/PolMine/topicanalysis?branch=master&svg=true)](https://ci.appveyor.com/project/PolMine/topicanalysis)
[![codecov](https://codecov.io/gh/PolMine/topicanalysis/branch/master/graph/badge.svg)](https://codecov.io/gh/PolMine/topicanalysis/branch/master)

## About

Using topic models, an unsupervised learning approach developed for information retrieval, has become common in the humanities and the social sciences. But in this disciplinary context, the methodological relocation of topic modelling requires the development of best practices and tools how validity can be ensured. The **topicanalysis** package offers a toolset to evaluate topic models, and to support validation by offering a nexus between quantitative and qualitative inquiry.

## Installation 

### Windows

Installation on Windows has not been tested at this stage, but should be possible. Installing the package from GitHub requires the devtools package. Note that an Installation of Rtools will be a prerequisite to get Rtools installed.

```{r, eval = FALSE}
devtools::install_github("PolMine/topicanalysis")
```

### macOS

Installing the topicmodels package may require to have the GNU Scientific Library installed (GSL). We recomment to use the brew package manager to meet this system requirement.

```{sh, eval = FALSE}
brew install gsl
```

The topicanalysis package is a GitHub-only package at this stage. Using the installation mechanism from the devtools package, you can install it as follows:

```{r, eval = FALSE}
devtools::install_github("PolMine/topicanalysis")
```


### Linux 

The package relies on the [topicmodels](https://CRAN.R-project.org/package=topicmodels) package which has the GNU Scientific Library (GSL) as a system requirement. Install it as follows.

```{sh, eval = FALSE}
sudo apt-get install libgsl-dev
```

```{r, eval = FALSE}
devtools::install_github("PolMine/topicanalysis")
```