---
title: "Using the 'topicanalysis'-package"
author: "Andreas Blätte (andreas.blaette@uni-due.de)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: topicmodelling.bibtex
vignette: >
  %\VignetteIndexEntry{Using the 'topicanalysis'-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---

## Purpose

Using topic models, a text mining technique originally developed for the purposes of information retrieval, has become a common technique in the social sciences [@Blätte2018]. The original algorithm, 'latent dirichlet allocation' (LDA) is the most commonly used topic model. Yet while there is a set of quantitative instruments to evaluate a topic model, there are not yet tools readily available for the qualitative evaluation of a topic model. The 'topicanalysis' package offers a workflow to integrate quantitative and qualitative analysis, and offers supplementary functionality.

## Installation

At this stage, the package is only available at GitHub.

```{r eval = FALSE}
devtools::install_github("PolMine/topicanalysis")
```


## Getting Started

```{r}
library(topicanalysis)
```

The package includes a sample LDA topicmodel for Germany's regional parliaments in Berlin ("Berliner Abgeordnetenhaus") and the Saarland ("Landtag des Saarlands").

```{r}
data(package = "topicanalysis")
```

[Lazy loading](https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Lazy-loading) of the data is delibarately not supported to keep the time to install the package minimal. We need to activate the data expressively.

```{r load_data}
data(BE_lda)
data(BE_labels)
```


## The 'Topicanalysis' Class

```{r}
BE <- Topicanalysis$new(topicmodel = BE_lda)
```

## Miscellaneous

```{r, fig.width = 5}
asylum_topic_no <- grep("Asyl", BE_labels)
dotplot(BE_lda, topic = asylum_topic_no, n = 10L)
```



## References 

